---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# rgee2

<!-- badges: start -->
<!-- badges: end -->

The goal of rgee2 is to ...

## Installation

You can install the development version of rgee2 from [GitHub](https://github.com/) with:

``` r
# install.packages("remotes")
remotes::install_github("rpkgs/rgee2")
```

## 网络代理

- **安装gcloud**
```R
# gcloud info --run-diagnostics
# C:/Users/kong/AppData/Roaming/gcloud/configurations/config_default
[proxy]
type = http
address = localhost
port = 1081
```

- **R语言设置**

**The following solution not working. Because we need to set proxy before R start, other than after.**
See <https://github.com/r-spatial/rgee/issues/73#issuecomment-1186549194> for details.

```R
Sys.setenv(https_proxy="http://127.0.0.1:1081")
Sys.setenv(http_proxy="http://127.0.0.1:1081")
```

- ### 1. RStudio uses `R.exe`

```bash
#subl  C:/Program Files/R/R-4.2.0/etc/Rcmd_environ
http_proxy="http://127.0.0.1:1081"
https_proxy="http://127.0.0.1:1081"
```

- ### 2. VScode uses `radian.exe`

```javascript
// code .vscode/settings.json
{
  "r.rterm.windows": "c:/ProgramData/Miniconda3/envs/gee/Scripts/radian.exe",
  "terminal.integrated.env.windows": {
    // "PATH": "${env:PATH}",
    "http_proxy":"http://127.0.0.1:1081",
    "https_proxy":"http://127.0.0.1:1081",
  },
}
```

```powershell
[Environment]::SetEnvironmentVariable("http_proxy", "http://127.0.0.1:1081", [System.EnvironmentVariableTarget]::User)
[Environment]::SetEnvironmentVariable("https_proxy", "http://127.0.0.1:1081", [System.EnvironmentVariableTarget]::User)
```

## Example

This is a basic example which shows you how to solve a common problem:

```{r example}
library(rgee2)
library(rgee)
ee_Initialize(drive = TRUE)
```

### Illustration by EAR5L data

```{r cars}
# bands = c('T', "Tdew", 'Pa', 'Rn', 'ET', 'U2')
year = 2020
month = 1
col <- ee$ImageCollection("ECMWF/ERA5_LAND/HOURLY")$
    filter(ee$filter$Filter$calendarRange(year, year, "year"))$
    filter(ee$filter$Filter$calendarRange(month, month, "month"))$
    select(0:4)
# print(col)

img = col$first()
print(img)
```

```{r, eval = FALSE}
ee_timestart(col) %>% head()
ee_timeend(col) %>% head()

ee_bandNames(col)
ee_bandNames(img)

ee_properties(col)
ee_aggregate_array(col, prop = "system:index")
```
