---
title: "Vegetation response to 2022 drought in China"
author: "Dongdong Kong, CUG, China"
date: '`r Sys.Date()`'
output: 
  html_document: 
    number_sections: true
runtime: shiny
---

# 介绍

农业干旱实时监测。

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
devtools::load_all()

library(magrittr)
library(shiny)
library(leaflet)
library(rgee)
library(rgee2)
library(rcolors)

library(leaflet.minicharts)
library(manipulateWidget)
library(leafsync)

# library(leaflet.extras2) # backends

str_num <- function(x, digits = 3) {
  fmt = sprintf("%%.%df", digits = 3)
  sprintf(fmt, x)
}
cal_p <- function(p, digits = 3) str_num(pnorm(p), digits)
cal_T <- function(p, digits = 2) str_num(1 / pnorm(p), digits)
```

# 数据与方法

## 数据

-   `MOD13A1.006`: <https://lpdaac.usgs.gov/products/mod13a1v006/>

> `MOD13A1.061`在2022年两个16-day缺失，因此未采用新版的`MOD13A1.061`数据。

## 方法

$$
VI\_norm_{year,k} = \frac{VI_{year,k}-mean_{k}}{sd_{k}}
$$

其中，下标$year$代表年，$year∈[2000, 2022]$；下标$k$为第$k$个16天，$k∈[1, 23]$；$mean_k$和$sd_k$分别为2000-2021年中每年第$k$个16天的VI的均值和标准差。

-   干旱的重现期

| $VI\_norm{year,k}$ | 概率$P(x <= x_0)$ | 重现期$T = 1 / P(x <= x_0)$ |
|--------------------|-------------------|-----------------------------|
| 1.0                | `r cal_p(1.0)`    | `r cal_T(1.0)`              |
| 0.5                | `r cal_p(0.5)`    | `r cal_T(0.5)`              |
| 0.0                | `r cal_p(0.0)`    | `r cal_T(0.0)`              |
| -0.5               | `r cal_p(-0.5)`   | `r cal_T(-0.5)`             |
| -1.0               | `r cal_p(-1.0)`   | `r cal_T(-1.0)`             |
| -1.5               | `r cal_p(-1.5)`   | `r cal_T(-1.5)`             |
| -2.0               | `r cal_p(-2.0)`   | `r cal_T(-2.0)`             |

You can embed Shiny inputs and outputs in your document. Outputs are automatically updated whenever inputs change. This demonstrates how a standard R plot can be made interactive by wrapping it in the Shiny `renderPlot` function. The `selectInput` and `sliderInput` functions create the input widgets used to drive the plot.

# 结果

```{r, echo=FALSE}
ee_init()
## global variables ------------------------------------------------------------
bands <- c("NDVI", "EVI", "DayOfYear", "SummaryQA")
col <- ee$ImageCollection("MODIS/006/MOD13A1")$
  select(bands)$
  filterDate("2000-01-01", "2022-12-31")

col <- col_add_dn_date(col, include.year = FALSE, chunksize = 16)
# ee_aggregate_array(col, "di")
col_clim <- col$filterDate("2000-01-01", "2021-12-31")
col_2022 <- col$filterDate("2022-01-01", "2022-12-31")

init = 0
# 根据doy进行aggregate，计算气候态均值
get_climatology <- function() {
  system.time(lst_mean <- ee_aggregate_list(col_clim, "di", "mean"))
  system.time(lst_sd <- ee_aggregate_list(col_clim, "di", "stdDev"))
  assign("lst_mean", lst_mean, .GlobalEnv)
  assign("lst_sd", lst_sd, .GlobalEnv)
}
get_climatology()
```

```{r, echo=FALSE}
get_NDVI_norm <- function(date = "2022-08-13", rm_cloud = TRUE) {
  img_raw = col$filterMetadata("date", "equals", date)$first()
  di = img_raw$get("di") %>% getInfo() %>% as.numeric()
  print(di)
  
  mean <- lst_mean[[di]]
  sd <- lst_sd[[di]]
  img_norm <- img_raw$select(0)$subtract(mean)$divide(sd)
  print(rm_cloud)
  
  if (rm_cloud) {
    mask = img_raw$select("SummaryQA")$neq(3L)
    img_norm = img_norm$updateMask(mask)
  }
  list(img_raw = img_raw, img_norm = img_norm)
}

draw_NDVI_norm <- function(img, delta = 1, title = "normalized NDVI") {
  color <- rcolors$MPL_RdYlGn
  vis_vi <- list(
    bands = c("NDVI"), palette = color,
    min = -delta, max = delta
  )
  # Map$centerObject(sf_prov$geometry, 7)
  Map$setCenter(110, 35, 4)
  Map$addLayer(img, vis_vi, title) +
    Map$addLegend(vis_vi, name = "VI_norm") +
    ee_draw_sf(sf_prov, "省界")
}

draw_VI_qc <- function(img) {
  # Parameters for visualization
  labels <- c("good", "marginal", "snow", "cloud")
  cols <- c("#999999", "#00BFC4", "#F8766D", "#C77CFF")
  vis_qc <- list(min = 0, max = 3, palette = cols, bands = "SummaryQA", values = labels)

  # Create interactive map
  m_qc <- Map$addLayer(img, vis_qc, "QC")
  # continous palette
  # Map$addLegend(vis_qc)
  
  # categorical palette
  lgd = Map$addLegend(vis_qc, name = "QC", color_mapping = "discrete")
  m_qc + lgd + 
    ee_draw_sf(sf_prov, "省界")
}

sf_prov = ee$FeatureCollection("users/kongdd/shp/China/bou2_4p_ChinaProvince")
ee_draw_sf <- function(shp, title = NULL, color = '000000', width=1.5) {
  empty = ee$Image()$byte()
  if (is.null(title)) title = shp$get("system:id") %>% getInfo() %>% basename()
  # Paint all the polygon edges with the same number and width, display.
  outline = empty$paint(featureCollection = shp, color = 1, width = width)
  Map$addLayer(outline, list(palette = color), title)
}
```

请选择想要查看的日期！

```{r NDVI_norm, echo=FALSE}
dates <- ee_systemtime(col_2022) %>% substr(1, 10)

color <- rcolors$MPL_RdYlGn
  delta = 1
  vis_vi <- list(
    bands = c("NDVI"), palette = color,
    min = -delta, max = delta
  )
  
selectInput("date",
    label = "Date",
    choices = dates, selected = dates[length(dates)]
  )

checkboxInput("rm_cloud", "Remove Cloud according to QC", TRUE)
```

Figure1. $NDVI\_norm$与$QC$空间分布

```{r, echo=FALSE}
# rmarkdown::render_delayed({
  renderLeaflet({
    # if (init == 0) {
    #   get_climatology() # load 
    #   init = 1
    # }
    eventReactive(c(input$date, input$rm_cloud), {
      l = get_NDVI_norm(input$date, input$rm_cloud)      
      m_vi = draw_NDVI_norm(l$img_norm)
      m_qc = draw_VI_qc(l$img_raw)
      m_vi | m_qc
    }, ignoreNULL = FALSE)()
  })  
#})
```

## Try about `ui.`

```{r, echo=FALSE}
renderLeaflet({
  eventReactive(c(input$date, input$rm_cloud), {
    l = get_NDVI_norm(input$date, input$rm_cloud)      
    m_vi = draw_NDVI_norm(l$img_norm)
    m_qc = draw_VI_qc(l$img_raw)
    combineWidgets(syncWith(m_vi, "one"), syncWith(m_qc, "one"))
    # sync(m_vi, m_qc)
  }, ignoreNULL = FALSE)()
})  
```

```{r, echo=FALSE}
renderLeaflet({
  eventReactive(c(input$date, input$rm_cloud), {
    l = get_NDVI_norm(input$date, input$rm_cloud)      
    m_vi = draw_NDVI_norm(l$img_norm)
    m_qc = draw_VI_qc(l$img_raw)
    sync(m_vi, m_qc)
  }, ignoreNULL = FALSE)()
})  
```

# TODO

-   [x] 添加中国省份信息；
-   [ ] 被云污染的地方明显偏低，不适合指示干旱
-   [ ] 测试reduceRegion功能，绘制时间序列图；

# Reference

1.  Zhang, Q., Xiao, M., Singh, V. P., & Li, J. (2012). Regionalization and spatial changing properties of droughts across the Pearl River basin, China. Journal of Hydrology, 472--473, 355--366. <https://doi.org/10.1016/j.jhydrol.2012.09.054>

2.  [Interactive Shiny Documents](http://rmarkdown.rstudio.com/authoring_shiny.html)
